Individual and Differential Harm in Redistricting

### 2022-04-05 paper/paper.Rmd
try abstract

---
title: Individual and Differential Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: |
      To whom correspondence should be addressed. 
      The authors thank participants of the Harvard American Politics 
      Research Workshop for helpful comments and discussion.
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Abstract here.
keywords:
  - representation
  - redistricting simulation
  - individual standing
bibliography: references.bib
biblio-style: apalike
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r nj-pairs, fig.cap="Scatterplots for all pairs of measures. Point lightness indicates the number of Democratic seats won (ranging from 7 (dark) to 10 (light)). The Democratic and Republican gerrymanders are shown with the blue and red lines and crosses. The dashed line indicates a value of zero. Below the diagonal, numbers indicate the absolute value of the correlation between variables.", fig.width=7, fig.height=7}
include_graphics(here("paper/figures/nj_pairs.pdf"))
```

>>>>

---
title: Individual and Differential Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: |
      To whom correspondence should be addressed. 
      The authors thank participants of the Harvard American Politics 
      Research Workshop for helpful comments and discussion.
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  We propose a unified framework for evaluating the impact of a districting plan on voters overall and in different groups. By aggregating the harm done to individual voters by their inability to elect a candiate of choice, and taking into account the space of counterfactual possibilities, we derive at a set of measures that flexibly adapts to local geographic constraints, different types of elections, and different groups of study.  The measures have connections to, and distinct advantages over, common redistricting metrics.  We provide recommendations for estimating these measures from historical election returns, and apply these methods to study partisan gerrymandering of New Jersey congressional districts and the racial impacts of district boundaries for primary elections for the Boston city council.
keywords:
  - representation
  - redistricting simulation
  - individual standing
bibliography: references.bib
biblio-style: apalike
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r nj-pairs, fig.cap="Scatterplots for all pairs of measures. Point lightness indicates the number of Democratic seats won at baseline (ranging from 7 (dark) to 10 (light)). The Democratic and Republican gerrymanders are shown with the blue and red lines and crosses. The dashed line indicates a value of zero. Below the diagonal, numbers indicate the absolute value of the correlation between variables.", fig.width=7, fig.height=7}
include_graphics(here("paper/figures/nj_pairs.pdf"))
```
